Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-02-09 template.tex
big update on simplification of final results

mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}

@@

r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right)

@@

Evaluating the derivative gives

@@

\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \label{eq:end1} \\
\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy} \label{eq:end2}

@@

\item Note that $I(x,0)$ has exact solutions:
I(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
I(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
\item To solve Eq. \ref{eq:end2}, the integral function is expanded in powers of $z_0$.  This is wise, given that the UHE-$\nu$ signal bandwidth will usually exceed that of a dipole receiver with response $r(t)$ and analytic signal $r_a(t)$.

>>>>

\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}

@@

r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right) \label{eq:withI}

@@

All that remains is to evaluate the integral
I(z,z_0) = \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy
Let $z = x+jy$, $dy = -jdz$, and $z_1 = x+jz_0$.  The integral becomes, as $R \to \infty$,
I(x,z_0) = \int_{x}^{x+jR} \frac{e^{z^2}}{z - z_1} dz
$I(x,z_0)$ can be evaluated via contour integration, with a rectangular contour that encloses the pole if $x > \Im\lbrace z_0\rbrace$.  Let $I_1$ extend from $(x,0)$ to ($x,jR)$.  Let $I_2$ extend from $(x,jR)$ to $(0,jR)$.  Let $I_3$ extend from $(0,jR)$ to $(0,0)$.  Finally, let $I_4$ extend from $(0,0)$ to $(x,0)$.  Note that $I_1 = I(x,z_0)$.  For the integral $I_2$, note that the exponential factor is proportional to $\exp(-R^2)$, while the denominator contains another factor of $R$.  Since $dz = dx$, the integrand goes as $\exp(-R^2)/R$, vanishing as $R \to \infty$.  For $I_3$, $x=0$.  Thus, it reduces to
I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y-z_0} dy
Let $y \to -y$, so that 
I_3 = - \int_{0}^{R} \frac{e^{-y^2}}{y+z_0} dy = -G(z_0)
The function $G(z_0)$ is known as the Goodwin-Staton integral.  $G(z_0)$ appears in radiation transport, neutron transport, and optical calculations.  It is commonly used in problems involving diffusion approximations, particularly in media with semi-infinite boundary conditions.  The final segment of the contour is
I_4 = \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
The sum of contour segments is $I_1 + I_2 + I_3 + I_4 = I_{\rm C}$, where $I_{\rm C}$ is given by the Cauchy integral formula: $2\pi j e^{z_1^2}$.  Solving for $I(x,z_0)$, we find
I(x,z_0) = 2\pi j e^{z_1^2} + G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
If $x < \Im\lbrace z_0\rbrace$,
I(x,z_0) = G(z_0) - \frac{j}{z_0}\int_{0}^{x} e^{x'^2} dx'
\end{equation} \\
Inserting this result into Eq. \ref{eq:withI},
r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(\frac{dA(x,z_0)}{dx}-\frac{j}{z_0}\frac{dD(x)}{dx} \right) \label{eq:ra_sa_1}
with

@@

A(x,z_0) &= 2\pi j e^{z_1^2} e^{-x^2} + G(z_0)e^{-x^2}, ~~ x > \Im \lbrace z_0 \rbrace\\
A(x,z_0) &= G(z_0)e^{-x^2}, ~~ x < \Im \lbrace z_0 \rbrace

@@

and
D(x) = e^{-x^2} \int_{0}^{x} e^{x'^2} dx'
What remains is to compute the magnitude of Eq. \ref{eq:ra_sa_1}.  Let the overall scale factor in Eq. \ref{eq:ra_sa_1} be $R_0 E_0 \sigma_t^2/\sqrt{\pi}$, let $z_0 = x_0 + j y_0$, and let $x>\Im\lbrace z_0\rbrace$.  Upon taking the magnitude, the quantity in parentheses generates four terms.  The first is
\frac{dA^{*}}{dx}\frac{dA}{dx} = \\ 16\pi^2|z_0|^2 e^{-4x y_0 - 2x_0^2-2y_0^2} \\ + 4G(z_0)x^2 e^{-2x^2} \\ + 16\pi G(z_0) x e^{-x^2}e^{-\gamma t} e^{-x_0^2+y_0^2} \\ \times \left(x_0\cos(2x_0(x-y_0)) - y_0\sin(2x_0(x-y_0)) \right)
The second is
\frac{1}{z_0^2}\left(\frac{dD(x)}{dx}\right)^2 = \frac{1}{z_0^2}\left(1-4xD(x)+4x^2D^2(x) \right)
The combination of the third and forth terms is
\frac{dD}{dx}\left\lbrace \frac{j}{z_0^{*}} \frac{dA}{dx} - \frac{j}{z_0} \frac{dA^{*}}{dx}\right\rbrace = \\
-\frac{2}{|z_0|^2} \frac{dD}{dx}\frac{d}{dx} ( -2\pi y_0 e^{-2xy_0} e^{y_0^2-x_0^2}\sin(2x_0(x-x_0)) \\
+ y_0G(z_0)e^{-x^2} \\
+ 2\pi x_0 e^{-2xy_0} e^{y_0^2-x_0^2}\cos(2x_0(x-x_0)) )
